---
title: "Vignette_01"
author: "Joowhan Song"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## My functions

```{r}
## function 1
# Calculate Mean, Variane, SD
# Computes the mean, variance and sd of a vector
x <- 1:10
func1 <- function(x){
  a = sum(x)/length(x)
  b = sum((x-a)^2)/length(x)
  c = sqrt(b)
  return(list(mean=a,var=b,sd=c))
}
func1(x)
```

```{r}
## function 2
# Calculate Mean, Variane, SD
# Computes the mean, variance and sd of a vector
x <- 1:10
func2 <- function(x){
  stopifnot(is.numeric(x))
  stopifnot(length(x)!=0)
  stopifnot(is.finite(x))
  stopifnot(!is.na(x))
  stopifnot(!is.nan(x))
  
  a = sum(x)/length(x)
  b = sum((x-a)^2)/length(x)
  c = sqrt(b)
  return(list(mean=a,var=b,sd=c))
}
```

```{r}
## function 3
# Computes the liklihood of a gamma distribution

n <- 30
set.seed(42)
x <- rgamma(n,shape = alpha)
interval <- mean(x) + c(-1,1)*3*sd(x)
interval <- pmax(mean(x)/1e3, interval)
func3 <- function(x){
  alpha <- pi
  log <- function(alpha)
    sum(dgamma(x, shape = alpha, log = TRUE))
  interval <- mean(x) + c(-1,1) * 3 * sd(x)
  interval <- pmax(mean(x) / 1e3, interval)
  
  oout<- optimize(log, maximum = TRUE, interval)
  return (oout$maximum)
}
func3(x)

```

```{r}
## fucntion 5
# Computes the weighted mean, var, sd
d <- read.table(url("http://www.stat.umn.edu/geyer/3701/data/q1p4.txt"),
    header = TRUE)
func4 <- function(d){
  
  a = sum(d$x * d$p)
  b = sum(((d$x - a)^2) * d$p)
  c = sqrt(b)
  return(list(mean=a,var=b,sd=c))
  
}
func4(d)
```

```{r}
## function 6
# Computes the weighted mean, var, sd with user checks

d <- read.table(url("http://www.stat.umn.edu/geyer/3701/data/q1p4.txt"),
    header = TRUE)
func5 <- function(d){
  
  stopifnot(is.numeric(d$x))
  stopifnot(is.numeric(d$p))
  
  stopifnot(length(d$x)!=0)
  stopifnot(length(d$p)!=0)
  
  stopifnot(is.finite(d$x))
  stopifnot(is.finite(d$p))
  
  stopifnot(!is.na(d$x))
  stopifnot(!is.na(d$p))
  
  stopifnot(!is.nan(d$x))
  stopifnot(!is.nan(d$p))
  
  stopifnot(all.equal(sum(d$p),1))
  
  a = sum(d$x * d$p)
  b = sum(((d$x - a)^2) * d$p)
  c = sqrt(b)
  return(list(mean=a,var=b,sd=c))
  
}
func5(d)
```

```{r}
## function 7
# Highlevel check function
x<-1:10
func6 <- function(x){
  
  tryCatch(stopifnot(is.numeric(x)), error=function(e){print("not numeric")})
  tryCatch(stopifnot(is.finite(x)), error=function(e){print("not finite")})
  tryCatch(stopifnot(length(x)!=0), error=function(e){print("has 0 length")})
  tryCatch(stopifnot(!is.nan(x)), error=function(e){print("NA or NAN")})
  tryCatch(stopifnot(!is.na(x)), error=function(e){print("NA or NAN")})
  
}
func6(x)
```

```{r}
## fucntion 8
# Computes the liklihood of a given distribution for data x

x1 <- scan(url("http://www.stat.umn.edu/geyer/3701/data/q1p3.txt"))
x2 <- scan(url("http://www.stat.umn.edu/geyer/3701/data/q1p7c.txt"))
x3 <- scan(url("http://www.stat.umn.edu/geyer/3701/data/q1p7b.txt"))

f1 <- function(theta,x) dgamma(x, shape = theta, log = TRUE)
f2 <- function(theta, x) dcauchy(x, location = theta, log = TRUE)
f3 <- function(theta, x) dbinom(x, 20, prob = 1 / (1 + exp(- theta)), log = TRUE)

func7 <- function(x, func, interval){
  
  f7 <- function(theta, x)
  {sum(func(theta, x))}
  
  oout<- optimize(f7, maximum = TRUE, interval, x=x)
  return(oout$maximum)
} 


  
func7(x1,f1,c(0,100))
func7(x2,f2,c(1,10))
func7(x3,f3,c(-100,100))

```
```{r}
## fucntion 9
# Computes matrix

load(url("http://www.stat.umn.edu/geyer/3701/data/q2p1.rda"))

func8 <- function(a,x)
{
  stopifnot(is.numeric(a))
  stopifnot(is.finite(a))
  stopifnot(is.numeric(x))
  res <- t(x)%*%solve(a)%*%x
  return(res)
}
func8(a,x)

```
```{r}
## function 10
# standardizes matrix

load(url("http://www.stat.umn.edu/geyer/3701/data/q2p3.rda"))

func9 <- function(x)
{
  if(nrow(x)==1){
    stop("number of row cannot be equal to 1")
  }
  res = (x-mean(x))/sd(x)
  return(res)
}

func9(a)


```

## Vignette Template

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
